---
title: "Data Analysis for Harming and Time Pressure"
author: "George Dewey, Hiroyasu Ando, Ryo Ikesu, Akihiro Nishi, TBD"
format: 
  pdf:
    toc: true
editor: visual
---

# Introduction

## Load required packages

```{r, message = F, warning = F}
library(tidyverse)
library(igraph)
library(lme4)
library(lmerTest)
library(DescTools)
library(data.table)
library(broom.mixed)
library(patchwork)
library(stringr)
library(ggpattern)
```

## Load required data

```{r}
## Original harming experiment - Experiment A
load("~/Documents/Projects/harming_esn/data/exp1/exp1data.Rdata")

## TP harming experiment - Experiment B
load("~/Documents/Projects/harming_esn/data/exp4/exp4data.Rdata")
```

## Create helper functions

```{r}
mean1 = function(x) {mean(x,na.rm=TRUE)}
median1 = function(x) {median(x, na.rm = TRUE)}
sd1 = function(x) {sd(x, na.rm = TRUE)}
se_mean = function(x) sd1(x)/sqrt(sum(is.na(x) == 0))
```

# Analysis

```{r}
exp1data = exp1data %>%
  mutate(behavior = case_when(behavior_coop == 1 ~ "C",
                              behavior_defect == 1 ~ "D",
                              behavior_punish == 1 ~ "P"),
         behavior_lag = case_when(behavior_coop_lag == 1 ~ "C",
                                  behavior_defect_lag == 1 ~ "D",
                                  behavior_punish_lag == 1 ~ "P")) 
```

## Descriptive Analysis

```{r}
exp1data %>%
  filter(round != 0) %>%
  nrow()

exp1data %>%
  filter(round != 0, is.na(behavior) == F) %>%
  nrow()
```

### Per-game characteristics

```{r, message = F}
# Players per game, min, max - Experiment 1
exp1data %>%
  filter(round >= 1) %>%
  group_by(game) %>%
  select(superid) %>%
  unique() %>%
  nrow()

exp1data %>%
  filter(round >= 1) %>%
  group_by(game) %>%
  select(superid) %>%
  unique() %>%
  summarize(n = n()) %>%
  summarize(`Mean Players` = mean(n),
            `Min Players` = min(n),
            `Max Players` = max(n))
```

```{r, message = F}
# Players per game, min, max - Experiment B
exp4data %>%
  filter(time_pressure == "Minus") %>% 
  group_by(game) %>%
  select(superid) %>%
  unique() %>%
  summarize(n = n()) %>%
  summarize(`Mean Players` = mean(n),
            `Min Players` = min(n),
            `Max Players` = max(n))
```
```{r}
exp4data %>%
  filter(time_pressure == "Plus", round > 0, behavior %in% c("C", "D", "P")) %>%
  nrow()
```

### Rate of timeout in Exp B, TP+

```{r}
exp4data %>%
  filter(time_pressure == "Plus", round > 0) %>%
  nrow() 

exp4data %>%
  filter(time_pressure == "Plus", round > 0) %>%
  select(superid, game, round, behavior, timeout, behaviorTime_sec)

1341/nrow(exp4data %>% filter(round > 0, time_pressure == "Plus"))
```

### Behavior breakdown

```{r}
# Behavior breakdown - Experiment A
data1_behavior_count = exp1data %>%
  filter(round >= 1) %>%
  group_by(behavior) %>%
  filter(behavior %in% c("C", "D", "P")) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(proportion = count/sum(count))

# Confidence Intervals 
data1_behavior_CI = MultinomCI(x = c(4878, 4336, 652), sides = "two.sided") %>%
  as_tibble()

data1_behavior_count
```

```{r}
# Behavior breakdown - Experiment B
exp4data %>%
  group_by(behavior) %>%
  filter(round > 0, behavior %in% c("C", "D", "P")) %>%
  nrow()

exp4data %>%
  group_by(behavior) %>%
  filter(round > 0, behavior %in% c("C", "D", "P")) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(proportion = count/sum(count)) 


MultinomCI(c(4185, 5790, 679), sides = "two.sided")
```

```{r}
# Behavior breakdown - Experiment B, TP-
exp4data_tp_minus_count = exp4data %>%
  group_by(behavior) %>%
  filter(time_pressure == "Minus", behavior %in% c("C", "D", "P")) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(proportion = count/sum(count))

exp4data_tp_minus_CI = MultinomCI(c(2013, 2893, 341), sides = "two.sided")

exp4data_tp_minus_count
```

```{r}
# Behavior breakdown - Experiment B, TP+
exp4data_tp_plus_count = exp4data %>%
  group_by(behavior) %>%
  filter(time_pressure == "Plus", behavior %in% c("C", "D", "P")) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(proportion = count/sum(count))

exp4data_tp_plus_CI = MultinomCI(c(2172, 2897, 338), sides = "two.sided")

exp4data_tp_plus_count
```

### Experiment A - Stratify by social environment

### Network characteristics

```{r}
# Network statistics
mean1(exp1data$degree)
min(exp1data$degree, na.rm = T)
max(exp1data$degree, na.rm = T)

mean1(exp4data$degree)
min(exp4data$degree, na.rm = T)
max(exp4data$degree, na.rm = T)
```

### Payoff

```{r}
mean1(exp1data$cumulativePayoff)
mean1(exp4data$cumulativePayoff)

exp4data %>%
  group_by(time_pressure) %>%
  summarize(mean_payoff = mean1(cumulativePayoff),
            se_mean_payoff = se_mean(cumulativePayoff))
```

## Decision time

```{r}
# Times per behavior
data1_times = exp1data %>%
  mutate(behavior = case_when(behavior_coop == 1 ~ "C",
                              behavior_defect == 1 ~ "D",
                              behavior_punish == 1 ~ "P")) %>%
  group_by(behavior) %>%
  filter(behavior %in% c("C", "D", "P")) %>%
  summarize(mean_dt = mean1(behaviorTime/1000),
            mean_dt_adjusted = mean1((behaviorTime - 4500)/1000),
            se_mean_dt = se_mean(behaviorTime/1000),
            UL_mean = mean_dt_adjusted + 1.96*se_mean_dt,
            LL_mean = mean_dt_adjusted - 1.96*se_mean_dt)
data1_times
```

# Figures

## Figure 2 - Behavior Distribution, Decision Times, and Punishment Mechanisms, Experiment 1

```{r}
# Fig 1A
exp1_fig1_data = bind_cols(data1_behavior_count, data1_behavior_CI, data1_times)[-7] 

names(exp1_fig1_data) = c("behavior", "count", "crude_prop", "adjusted_prop", "LL_prop", "UL_prop",
                          "mean_dt", "recentered_mean_dt", "se_mean_dt", "UL_mean_dt", "LL_mean_dt")
exp1_fig1_data = exp1_fig1_data %>% 
  mutate(behavior = case_match(behavior,
                               "C" ~ "Cooperation", 
                               "D" ~ "Defection",
                               "P" ~ "Punishment"))
```

```{r}
exp1_fig1_A = exp1_fig1_data %>%
  ggplot() +
  aes(x = behavior, y = adjusted_prop, fill = behavior) +
  geom_bar(stat = "identity", width = 0.75, alpha = 0.5) +
  geom_errorbar(aes(ymin = LL_prop, ymax = UL_prop, color = factor(behavior)), width = 0) +
  theme_classic() +
  scale_y_continuous(limits = c(0, 0.6), breaks = seq(0, 0.6, by = 0.2), expand = c(0, 0)) +
  ylab("Proportion") +
  scale_fill_manual(values = c("#00A5CF", "#FFBF00", "#574AE2")) +
  scale_color_manual(values = c("dodgerblue4", "darkorange3", "#574AE2")) +
  labs(tag = "A") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(size = 9),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank())
exp1_fig1_A
```

```{r}
exp1_fig1_B = exp1_fig1_data %>%
  ggplot() +
  aes(x = behavior, y = recentered_mean_dt, fill = behavior) +
  geom_bar(stat = "identity", width = 0.75, alpha = 0.5) +
  geom_errorbar(aes(ymin = recentered_mean_dt - 1.96*se_mean_dt, 
                    ymax = recentered_mean_dt + 1.96*se_mean_dt, 
                    color = factor(behavior)), width = 0) +
  theme_classic() +
  scale_y_continuous(limits = c(0, 8.5), breaks = seq(0, 8, by = 2), expand = c(0, 0)) +
  ylab("Decision time \n (seconds)")+
  scale_fill_manual(values = c("#00A5CF", "#FFBF00", "#574AE2")) +
  scale_color_manual(values = c("dodgerblue4", "darkorange3", "#574AE2")) +
  labs(tag = "B") + 
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(size = 9),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank())
exp1_fig1_B
```

```{r}
exp1data_NR = exp1data %>% 
  group_by(punish_type_NR) %>%
  count() %>%
  ungroup() %>%
  mutate(punish_type = "NR",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_NR == 1)  %>%
  select(punish_type, n, total, perc, se_perc)

exp1data_IA = exp1data %>% 
  group_by(punish_type_IA) %>%
  count() %>%
  ungroup() %>%
  mutate(punish_type = "IA",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_IA == 1)  %>%
  select(punish_type, n, total, perc, se_perc)

exp1data_CR = exp1data %>% 
  group_by(punish_type_CR) %>%
  count() %>%
  ungroup() %>%
  mutate(punish_type = "CR",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_CR == 1)  %>%
  select(punish_type, n, total, perc, se_perc)

exp1data_U = exp1data %>% 
  group_by(punish_type_U) %>%
  count() %>%
  ungroup() %>%
  mutate(punish_type = "U",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_U == 1)  %>%
  select(punish_type, n, total, perc, se_perc)

figS1data = bind_rows(exp1data_CR, exp1data_IA, exp1data_NR, exp1data_U)

figS1data = figS1data %>%
  mutate(perc_LL = perc - 1.96*se_perc,
         perc_UL = perc + 1.96*se_perc)
figS1data
```

```{r}
# Decision times by punish type

exp1data_NR_times = exp1data %>% 
  filter(punish_type_NR == 1, behavior_punish == 1) %>%
  summarize(mean_dt = mean1(behaviorTime_sec - 4.5),
            se_mean_dt = se_mean(behaviorTime_sec - 4.5)) %>%
  mutate(punish_type = "NR",
           mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp1data_IA_times = exp1data %>% 
  filter(punish_type_IA == 1, behavior_punish == 1) %>%
  summarize(mean_dt = mean1(behaviorTime_sec - 4.5),
            se_mean_dt = se_mean(behaviorTime_sec - 4.5),
) %>%
  mutate(punish_type = "IA",   mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp1data_CR_times = exp1data %>% 
  filter(punish_type_CR == 1, behavior_punish == 1) %>%
  summarize(mean_dt = mean1(behaviorTime_sec - 4.5),
            se_mean_dt = se_mean(behaviorTime_sec - 4.5)) %>%
  mutate(punish_type = "CR",
           mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp1data_U_times = exp1data %>% 
  filter(punish_type_U == 1, behavior_punish == 1) %>%
  summarize(mean_dt = mean1(behaviorTime_sec - 4.5),
            se_mean_dt = se_mean(behaviorTime_sec - 4.5)) %>%
  mutate(punish_type = "U",
         mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp1data_punish_types_times = bind_rows(exp1data_NR_times, 
                                        exp1data_CR_times,
                                        exp1data_IA_times, 
                                        exp1data_U_times) %>% select(punish_type, mean_dt, se_mean_dt, mean_LL, mean_UL)
fig1data = figS1data %>%
  left_join(exp1data_punish_types_times, by = "punish_type") %>%
  mutate(punish_type = case_match(punish_type,
             "CR" ~ "Copying/retaliation",
             "IA" ~ "Inequality aversion",
             "NR" ~ "Negative reinforcement",
             "U" ~ "Unclassified")) %>%
  mutate(punish_type_fct = factor(punish_type, levels = c("Copying/retaliation", "Negative reinforcement", "Inequality aversion", "Unclassified")))
```

```{r}
exp1_fig1_C = fig1data %>%
  ggplot(aes(x = punish_type_fct, y = perc, fill = punish_type_fct)) +
  geom_bar(position = "dodge", stat = "identity", alpha = 0.5, show.legend = F) +
  geom_errorbar(aes(ymin = perc + 1.96*se_perc, 
                    ymax = perc - 1.96*se_perc,
                    width = 0),
                color = "purple4",
                position = position_dodge(.9),
                show.legend = F) +
  scale_fill_manual(values = c("Copying/retaliation" = "plum3", "Negative reinforcement" = "mediumslateblue", "Inequality aversion" = "mediumpurple3", "Unclassified" = "orchid4"),  guide = "none") +
  scale_color_manual(guide = "none") +
  scale_x_discrete(labels = c("Copying/\nretaliation", "Negative\nreinforcement", "Inequality\naversion", "Unclassified")) +
  scale_y_continuous(limits = c(0, 0.05), expand = c(0, 0)) +
  ylab("Proportion") +
  xlab("") +
  labs(tag = "C") +
  theme_classic() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank(),
        axis.text.x = element_text(size = 8),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank()) 
exp1_fig1_C
```
```{r}
exp1_fig1_D = fig1data %>%
  ggplot(aes(x = punish_type_fct, y = mean_dt, fill = punish_type_fct)) +
  geom_bar(stat = "identity", width = 0.75,  alpha = 0.5) +
  geom_errorbar(aes(ymin = mean_LL, 
                    ymax = mean_UL),
                color = "purple4", width = 0) +
  theme_classic() +
  scale_y_continuous(limits = c(0, 8.5), breaks = seq(0, 8, by = 2), expand = c(0, 0)) +
  ylab("Decision time \n (seconds)")+
  scale_fill_manual(values = c("Copying/retaliation" = "plum3", 
                               "Negative reinforcement" = "mediumslateblue", 
                               "Inequality aversion" = "mediumpurple3", 
                               "Unclassified" = "orchid4"), guide = "none") +
  scale_x_discrete(labels = c("Copying/\nretaliation", "Negative\nreinforcement", "Inequality\naversion", "Unclassified")) +
  scale_color_manual(guide = "none") +
  theme_classic() +
  labs(tag = "D") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(size = 8),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank())
exp1_fig1_D
```

### Main
```{r}
(exp1_fig1_A + exp1_fig1_B)/ (exp1_fig1_C + exp1_fig1_D)

ggsave(filename = "~/Documents/Projects/harming_esn/figures/fig2.png", width = 8, height = 8, units = "in")
```

## Figure 3 - Behavior Distribution, Decision Times, and Punishment Mechanisms, Experiment 2

```{r}
exp4data_tp_plus_count = exp4data %>%
  group_by(behavior) %>%
  filter(time_pressure == "Plus", behavior %in% c("C", "D", "P")) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(proportion = count/sum(count))

exp4data_tp_plus_CI = MultinomCI(c(2172, 2897, 338), sides = "two.sided")

exp4data_tp_plus_times = exp4data %>%
  group_by(behavior) %>%
  filter(time_pressure == "Plus", behavior %in% c("C", "D", "P")) %>%
  summarize(mean_dt = mean1(behaviorTime/1000),
            se_mean_dt = se_mean(behaviorTime/1000),
            LL_mean = mean_dt - 1.96*se_mean_dt,
            UL_mean = mean_dt + 1.96*se_mean_dt)

exp4data_tp_minus_count = exp4data %>%
  group_by(behavior) %>%
  filter(time_pressure == "Minus", behavior %in% c("C", "D", "P")) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(proportion = count/sum(count))

exp4data_tp_minus_times = exp4data %>%
  group_by(behavior) %>%
  filter(time_pressure == "Minus", behavior %in% c("C", "D", "P")) %>%
  summarize(mean_dt = mean1(behaviorTime/1000),
            se_mean_dt = se_mean(behaviorTime/1000),
            LL_mean = mean_dt - 1.96*se_mean_dt,
            UL_mean = mean_dt + 1.96*se_mean_dt)

exp4data_tp_minus_CI = MultinomCI(c(2013, 2893, 341), sides = "two.sided")

exp4_tp_plus_fig3_data = bind_cols(exp4data_tp_plus_count, exp4data_tp_plus_CI, exp4data_tp_plus_times)[-7]
names(exp4_tp_plus_fig3_data) = c("behavior", "count", "crude_prop", 
                                  "adjusted_prop", "LL_prop", "UL_prop", "mean_dt", 
                                  "se_mean_dt", "LL_mean_dt", "UL_mean_dt")
exp4_tp_plus_fig3_data$setting = "TP+"

exp4_tp_minus_fig3_data = bind_cols(exp4data_tp_minus_count, exp4data_tp_minus_CI, exp4data_tp_minus_times)[-7]
names(exp4_tp_minus_fig3_data) = c("behavior", "count", "crude_prop", 
                                  "adjusted_prop", "LL_prop", "UL_prop", "mean_dt", 
                                  "se_mean_dt", "LL_mean_dt", "UL_mean_dt")

exp4_tp_minus_fig3_data$setting = "TP-"
fig3data = bind_rows(exp4_tp_minus_fig3_data, exp4_tp_plus_fig3_data)
fig3data = fig3data %>%
  mutate(behavior = case_match(behavior, "C" ~ "Cooperation", "D" ~ "Defection", "P" ~ "Punishment"))

fig3data
```
### Main
```{r}
fig3A = fig3data %>%
  ggplot(aes(x = behavior, y = adjusted_prop, fill = behavior, pattern = setting)) +
  geom_bar_pattern(position = "dodge", stat = "identity", alpha = 0.5, 
                   pattern_density = 0.4, pattern_color = "white", 
                   pattern_shape = 3) +
  geom_errorbar(aes(ymin = LL_prop, 
                    ymax = UL_prop,
                    color = behavior,
                    width = 0),
                position = position_dodge(.9),
                show.legend = F) +
  scale_pattern_manual(values = c("none", "pch")) +
  scale_fill_manual(values = c("Cooperation" = "#00A5CF", "Defection" = "#FFBF00", "Punishment" = "#574AE2")) +
  scale_color_manual(values = c("dodgerblue4", "darkorange3", "#574AE2")) +
  scale_y_continuous(limits = c(0, 0.65), expand = c(0, 0)) +
  guides(color = "none", fill = "none", pattern = guide_legend(title = "Setting")) +
  ylab("Proportion") +
  xlab("") +
  theme_classic() +
  labs(tag = "A") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text.x = element_text(size = 10),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "bottom",
        legend.key.size = unit(1, "cm"),
        legend.key = element_rect(fill = "#574AE2", color = NA)) +
  annotate("text", x = 1:3, 
           y = c(0.46, 0.61, 0.12), 
           label = c("italic(p) == 0.661", "italic(p) == 0.758", "italic(p) == 0.475"), 
           parse = T) 
fig3A
```
```{r}
fig3B = fig3data %>%
  ggplot() +
  aes(x = behavior, y = mean_dt, fill = behavior, pattern = setting) +
  geom_bar_pattern(stat = "identity", width = 0.75, alpha = 0.5, 
                   position = "dodge",
                   pattern_density = 0.4, 
                   pattern_color = "white", 
                   pattern_shape = 3, show.legend = F) +
  geom_errorbar(aes(ymin = mean_dt - se_mean_dt, 
                    ymax = mean_dt + se_mean_dt, 
                    color = factor(behavior)), 
                    position = position_dodge(0.75),
                    width = 0,
                show.legend = F) +
  geom_hline(yintercept = 3, color = "red2", alpha = 0.3) +
  theme_classic() +
  scale_pattern_manual(values = c("none", "pch")) +
  scale_y_continuous(limits = c(0, 5), expand = c(0, 0)) +
  scale_x_discrete(limits = c("Cooperation", "Defection", "Punishment")) +
  ylab("Decision time \n (seconds)")+
  scale_fill_manual(values = c("#00A5CF", "#FFBF00", "#574AE2")) +
  scale_color_manual(values = c("dodgerblue4", "darkorange3", "#574AE2")) +
  labs(tag = "B") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(size = 10),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank()) +
    annotate("text", x = 1:3, 
           y = c(3.45, 3.25, 4.25), 
           label = c(rep(expression(paste(italic("p")," < 0.0001")), 3)))

fig3B
```

```{r}
fig3A + fig3B +
  plot_annotation(tag_levels = c("A", "B")) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom") 

ggsave(filename = "~/Documents/Projects/harming_esn/figures/fig3.png", width = 7, height = 5, units = "in")
```

## Figure 4 - Punishment Mechanism Decision Times, Experiment 2

```{r}
# Get the frequencies stratified by TP status and by punishment type
exp4data = exp4data %>%
  mutate(punish_type_U = ifelse(is.na(punish_type_CR) == 1 & is.na(punish_type_NR) == 1 | is.na(punish_type_IA) == 1 & is.na(punish_type_U) == 1, 1, punish_type_U),
         punish_type_CR = ifelse(punish_type_U == 1, 0, punish_type_CR),
         punish_type_NR = ifelse(punish_type_U == 1, 0, punish_type_NR),
         punish_type_IA = ifelse(punish_type_U == 1, 0, punish_type_IA))
                    

fig4_tp_minus_CR = exp4data %>% 
  filter(time_pressure == "Minus") %>%
  group_by(punish_type_CR) %>%
  count() %>%
  ungroup() %>%
  mutate(setting = "TP-",
         punish_type = "CR",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_CR == 1)  %>%
  select(setting, punish_type, n, total, perc, se_perc)

fig4_tp_minus_IA = exp4data %>% 
  filter(time_pressure == "Minus") %>%
  group_by(punish_type_IA) %>%
  count() %>%
  ungroup() %>%
  mutate(setting = "TP-",
         punish_type = "IA",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_IA == 1)  %>%
  select(setting, punish_type, n, total, perc, se_perc)

fig4_tp_minus_NR = exp4data %>% 
  filter(time_pressure == "Minus") %>%
  group_by(punish_type_NR) %>%
  count() %>%
  ungroup() %>%
  mutate(setting = "TP-",
         punish_type = "NR",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_NR == 1)  %>%
  select(setting, punish_type, n, total, perc, se_perc)

fig4_tp_minus_U = exp4data %>% 
  filter(time_pressure == "Minus") %>%
  group_by(punish_type_U) %>%
  count() %>%
  ungroup() %>%
  mutate(setting = "TP-",
         punish_type = "U",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_U == 1)  %>%
  select(setting, punish_type, n, total, perc, se_perc)

fig4_tp_minus_data = bind_rows(fig4_tp_minus_CR, fig4_tp_minus_IA, fig4_tp_minus_NR, fig4_tp_minus_U)
```

```{R}
fig4_tp_Plus_CR = exp4data %>% 
  filter(time_pressure == "Plus") %>%
  group_by(punish_type_CR) %>%
  count() %>%
  ungroup() %>%
  mutate(setting = "TP+",
         punish_type = "CR",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_CR == 1)  %>%
  select(setting, punish_type, n, total, perc, se_perc)

fig4_tp_Plus_IA = exp4data %>% 
  filter(time_pressure == "Plus") %>%
  group_by(punish_type_IA) %>%
  count() %>%
  ungroup() %>%
  mutate(setting = "TP+",
         punish_type = "IA",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_IA == 1)  %>%
  select(setting, punish_type, n, total, perc, se_perc)

fig4_tp_Plus_NR = exp4data %>% 
  filter(time_pressure == "Plus") %>%
  group_by(punish_type_NR) %>%
  count() %>%
  ungroup() %>%
  mutate(setting = "TP+",
         punish_type = "NR",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_NR == 1)  %>%
  select(setting, punish_type, n, total, perc, se_perc)

fig4_tp_Plus_U = exp4data %>% 
  filter(time_pressure == "Plus") %>%
  group_by(punish_type_U) %>%
  count() %>%
  ungroup() %>%
  mutate(setting = "TP+",
         punish_type = "U",
         total = sum(n),
         perc = n/sum(n),
         se_perc = sqrt((perc*(1-perc))/total)) %>%
  filter(punish_type_U == 1)  %>%
  select(setting, punish_type, n, total, perc, se_perc)

fig4_tp_Plus_data = bind_rows(fig4_tp_Plus_CR, fig4_tp_Plus_IA, fig4_tp_Plus_NR, fig4_tp_Plus_U)

exp4data_combined = bind_rows(fig4_tp_minus_data, fig4_tp_Plus_data)

exp4data_combined
```

```{r}
exp4data_plus_NR_times = exp4data %>% 
  filter(punish_type_NR == 1, 
         behavior_punish == 1, 
         time_pressure == "Plus") %>%
  summarize(mean_dt = mean1(behaviorTime_sec),
            se_mean_dt = se_mean(behaviorTime_sec)) %>%
  mutate(punish_type = "NR",
         setting = "TP+",
           mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp4data_plus_CR_times = exp4data %>% 
  filter(punish_type_CR == 1, 
         behavior_punish == 1, 
         time_pressure == "Plus") %>%
  summarize(mean_dt = mean1(behaviorTime_sec),
            se_mean_dt = se_mean(behaviorTime_sec)) %>%
  mutate(punish_type = "CR",
         setting = "TP+",
         mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp4data_plus_IA_times = exp4data %>% 
  filter(punish_type_IA == 1, 
         behavior_punish == 1, 
         time_pressure == "Plus") %>%
  summarize(mean_dt = mean1(behaviorTime_sec),
            se_mean_dt = se_mean(behaviorTime_sec)) %>%
  mutate(punish_type = "IA",
                  setting = "TP+",
           mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp4data_plus_U_times = exp4data %>% 
  filter(punish_type_U == 1, 
         behavior_punish == 1, 
         time_pressure == "Plus") %>%
  summarize(mean_dt = mean1(behaviorTime_sec),
            se_mean_dt = se_mean(behaviorTime_sec)) %>%
  mutate(punish_type = "U",
         setting = "TP+",
         mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp4data_minus_NR_times = exp4data %>% 
  filter(punish_type_NR == 1, 
         behavior_punish == 1, 
         time_pressure == "Minus") %>%
  summarize(mean_dt = mean1(behaviorTime_sec),
            se_mean_dt = se_mean(behaviorTime_sec)) %>%
  mutate(punish_type = "NR",
                  setting = "TP-",
           mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp4data_minus_CR_times = exp4data %>% 
  filter(punish_type_CR == 1, 
         behavior_punish == 1, 
         time_pressure == "Minus") %>%
  summarize(mean_dt = mean1(behaviorTime_sec),
            se_mean_dt = se_mean(behaviorTime_sec)) %>%
  mutate(punish_type = "CR",
         setting = "TP-",
        mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp4data_minus_IA_times = exp4data %>% 
  filter(punish_type_IA == 1, 
         behavior_punish == 1, 
         time_pressure == "Minus") %>%
  summarize(mean_dt = mean1(behaviorTime_sec),
            se_mean_dt = se_mean(behaviorTime_sec)) %>%
  mutate(punish_type = "IA",
         setting = "TP-",
         mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp4data_minus_U_times = exp4data %>% 
  filter(punish_type_U == 1, 
         behavior_punish == 1, 
         time_pressure == "Minus") %>%
  summarize(mean_dt = mean1(behaviorTime_sec),
            se_mean_dt = se_mean(behaviorTime_sec)) %>%
  mutate(punish_type = "U",
         setting = "TP-",
         mean_LL = mean_dt - 1.96*se_mean_dt,
         mean_UL = mean_dt + 1.96*se_mean_dt) 

exp4data_times = bind_rows(exp4data_minus_CR_times, exp4data_minus_IA_times, exp4data_minus_NR_times, exp4data_minus_U_times, exp4data_plus_CR_times, exp4data_plus_IA_times, exp4data_plus_NR_times, exp4data_plus_U_times)
```

```{r}
exp4_times_old = exp4data_times %>%
  ggplot(aes(x = punish_type, y = mean_dt, fill = setting)) +
  geom_bar(position = "dodge", stat = "identity", alpha = 0.5, show.legend = T) +
  geom_errorbar(aes(ymin = mean_LL,
                    ymax = mean_UL,
                    color = factor(setting),
                    width = 0),
                position = position_dodge(.9),
                show.legend = F) +
  scale_fill_manual(values = c("slategray2", "goldenrod2"),
                    labels = c("TP-", "TP+"))+
  scale_color_manual(values = c("dodgerblue4", "darkorange3"), guide = "none") +
  scale_y_continuous(limits = c(0, 6), expand = c(0, 0)) +
  ylab("Decision time \n (seconds)") +
  xlab("") +
  theme_classic() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank()) 

exp4data_combined
```

### Main

```{r}
# Create the combined figure
exp4data_combined = exp4data_combined %>%
         mutate(punish_type_fct = factor(punish_type, levels = c("CR", "NR", "IA", "U")))
         
exp4data_combined %>%
  ggplot(aes(x = punish_type_fct, y = perc, fill = punish_type_fct, pattern = setting)) +
  geom_bar_pattern(position = "dodge", stat = "identity", alpha = 0.5, 
                   pattern_density = 0.25, pattern_color = "white", 
                   pattern_shape = 3) +
  geom_errorbar(aes(ymin = perc + 1.96*se_perc, 
                    ymax = perc - 1.96*se_perc,
                    width = 0),
                    color = "purple4",
                position = position_dodge(.9),
                show.legend = F) +
  scale_pattern_manual(values = c("none", "pch")) +
  guides(color = "none", fill = "none", pattern = guide_legend(title = "Setting")) +
  annotate("text", x = 1:4, 
           y = c(0.025, 0.0425, 0.045, 0.02), 
           label = c("italic(p) == 0.889", "italic(p) == 0.629", "italic(p) == 0.435", "italic(p) == 0.649"), 
           parse = T) +
  scale_fill_manual(values = c("CR" = "plum3", 
                               "NR" = "mediumslateblue", 
                               "IA" = "mediumpurple3", 
                               "U" = "orchid4"), 
                    limits = c("CR", "NR", "IA", "U"),
                    guide = "none") +
  scale_x_discrete(labels = c("Copying/\nretaliation", "Negative\nreinforcement", "Inequality\naversion", "Unclassified")) +
  scale_y_continuous(limits = c(0, 0.05), expand = c(0, 0)) +
  ylab("Proportion") +
  xlab("") +
  theme_classic() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "bottom",
        legend.key.size = unit(1, "cm"),
        legend.key = element_rect(fill = "#574AE2", color = NA),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank()) 

ggsave(filename = "~/Documents/Projects/harming_esn/figures/fig4.png", width = 7, height = 5, units = "in")
```

## Figure S2 - Distribution of Decision Times, Experiment 1

```{r}
exp1data %>%
  filter(is.na(behaviorTime_sec) == 0) %>%
  ggplot(aes(x = behaviorTime_sec, color = behavior)) +
  geom_density(adjust = 2, key_glyph = "path") +
  geom_vline(xintercept = 3, color = "red2", linetype = "dashed") +
  theme_classic() +
  labs(color = "Behavior") +
  xlab("Decision Time (sec)") +
  scale_x_log10(limits = c(1, 110),breaks = c(1, 10, 100), 
                name = "Decision Time (sec)") +
  scale_y_continuous(limits = c(0, 1.3), name = "Density") + 
  scale_color_manual(labels = c("Cooperation", "Defection", "Punishment"),
                     values = c("#00A5CF", "#FFBF00", "#574AE2"), guide = "none") +
  guides(colour=guide_legend(title = NULL)) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = c(0.9, 0.9),
        legend.title = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank()) 

ggsave(filename = "~/Documents/Projects/harming_esn/figures/figS2.png", width = 7, height = 5, units = "in")
```

# Regression modeling

## Global model

```{r}
m1 = glmer(behavior_punish ~ showScore + behavior_coop_lag + local_rate_coop_lag + behavior_punish_lag + local_rate_punish_lag + factor(round) + (1|game) + (1|superid), data = exp1data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))

tidy(m1, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(6) 
```

## Punishment vs. time pressure

```{r}
m2 = glmer(behavior_punish ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))

summary(m2)

exp4data %>% filter(round > 0, is.na(behavior) == F) %>%
  nrow()

tidy(m2, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(3) 
# p = 0.475
```

## Cooperation vs. time pressure

```{r}
m2.1 = glmer(behavior_coop ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))
summary(m2.1)

tidy(m2.1, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(4) 
# p = 0.661
```

## Defection vs. time pressure

```{r}
m2.2 = glmer(behavior_defect ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))

summary(m2.2)

tidy(m2.2, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(3) 

# p = 0.663
```

## Decision times vs. time pressure (not useful)

```{r}
model_dt_coop = lmer(behaviorTime_sec ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0, behavior_coop == 1))
summary(model_dt_coop)
```

```{r}
model_dt_def = lmer(behaviorTime_sec ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0, behavior_defect == 1))
summary(model_dt_def)
```

```{r}
model_dt_pun = lmer(behaviorTime_sec ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0, behavior_punish == 1))
summary(model_dt_pun)
```

## Punishment mechanisms vs. time pressure

### Punishment for copying/retaliation

```{r}
m3.1 = glmer(punish_type_CR ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))

summary(m3.1)

tidy(m3.1, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(3) 
# p = 0.891
```

```{r}
m3.1 = glmer(punish_type_CR ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))

summary(m3.1)

tidy(m3.1, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(3) 
```

```{r}
m3.2 = glmer(punish_type_NR ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))

summary(m3.2)

tidy(m3.2, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(3) 
# p = 0.634
```

```{r}
m3.3 = glmer(punish_type_IA ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))

tidy(m3.3, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(3) 
# p = 0.440
```
```{r}
m3.4 = glmer(punish_type_U ~ time_pressure + round + (1|game) + (1|superid),  data = exp4data %>% filter(round > 0), family = binomial, nAGQ=0, control = glmerControl(optimizer = c("bobyqa"), optCtrl=list(maxfun=2e5), calc.derivs=FALSE))

summary(m3.4)

tidy(m3.4, conf.int=TRUE, exponentiate=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 5)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(3) 
# p = 0.645
```

## Decision time as the outcome

### Exp 1 - Cooperation as reference

```{r}
exp1data = exp1data %>%
  mutate(behaviorTime_sec_adj = behaviorTime_sec - 4.5)
m4 = lmer(behaviorTime_sec_adj ~ behavior + round + (1|game) + (1|superid), data = exp1data)
summary(m4)
```

### Exp 1 - Defection as reference

```{r}
m4_1 = lmer(behaviorTime_sec_adj ~ factor(behavior, levels = c("D", "C", "P")) + round + (1|game) + (1|superid), data = exp1data)
summary(m4_1)
```

### Exp 1 - Comparing the punishment mechanisms

```{r}
m4_2 = lmer(behaviorTime_sec_adj ~ punish_type_NR + punish_type_IA + punish_type_U + round + (1|game) + (1|superid), data = exp1data %>% filter(behavior_punish == 1))
summary(m4_2)
tidy(m4_2, conf.int=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(8) 
```

### Comparing U vs all others

```{r}
m4_3 = lmer(behaviorTime_sec_adj ~ punish_type_U + punish_type_CR + punish_type_NR + punish_type_IA + round + (1|game) + (1|superid), data = exp1data %>%
  filter(behavior_punish == 1))
summary(m4_3)
```



## Exp B - Controlling for time pressure

```{r}
exp4_tp_plus = exp4data %>% filter(time_pressure == "Plus")
exp4_tp_minus = exp4data %>% filter(time_pressure == "Minus")

m5a = lmer(behaviorTime_sec ~ behavior + round + (1|game) + (1|superid), data = exp4_tp_plus %>% filter(round > 0))
summary(m5a)
tidy(m5a, conf.int=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(8) 
```

```{r}
m5b = lmer(behaviorTime_sec ~ behavior + round + (1|game) + (1|superid), data = exp4_tp_minus %>% filter(round > 0))

summary(m5b)

tidy(m5b, conf.int=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(8) 

```

# Exp A - Regression model with and without punishment in round t-1

```{r}
exp1data = exp1data %>%
  mutate(last_punished = ifelse(local_rate_punish_lag > 0, 1, 0))
m13 = lmer(behaviorTime_sec_adj ~ round + last_punished +
             (1|game) + (1|superid), data = exp1data %>% filter(behavior_punish == 1))

summary(m13)
```

## Exp B, TP-: Regression model with and without punishment

```{r}
exp4data_minus_lp = exp4data %>%
  mutate(last_punished = ifelse(local_rate_punish_lag > 0, 1, 0)) %>%
  filter(behavior_punish == 1, time_pressure == "Minus")
exp4data_plus_lp = exp4data %>%
  mutate(last_punished = ifelse(local_rate_punish_lag > 0, 1, 0)) %>%
  filter(behavior_punish == 1, time_pressure == "Plus")
m15 = lmer(behaviorTime_sec ~ last_punished + round + (1|game) + (1|superid), data = exp4data_plus_lp)

summary(m15)

tidy(m15, conf.int=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(8) 
```

```{r}
m16 = lmer(behaviorTime_sec ~ behavior + round + (1|game) + (1|superid), data = exp4_tp_minus_last_nopunish)
summary(m16)
tidy(m16, conf.int=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(8) 
```

## Exp B, TP+: Regression model with and without punish in last round

```{r}
m17 = lmer(log10(behaviorTime_sec) ~ behavior + round + (1|game) + (1|superid), data = exp4_tp_plus_last_punished)

summary(m17)
tidy(m17, conf.int=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(8) 
```

```{r}
m18 = lmer(log10(behaviorTime_sec) ~ behavior + round + (1|game) + (1|superid), data = exp4_tp_plus_last_nopunish)

summary(m18)

tidy(m18, conf.int=TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Term = term, Estimate = estimate, 
         LL = conf.low, UL = conf.high, p = p.value) %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  select(Term, Estimate, LL, UL, p) %>%
  head(8) 
```
